Arrows for Parallel Computations

### 2017-11-24 paper/content/benchmarks.tex
initial version of all worst benchmarks

\begin{table}[]
\centering
\label{my-label}
\begin{subtable}[t]{.5\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{l R{1cm} R{1.3cm} R{1.3cm}}
		% \multicolumn{3}{c}{worst Sudoku Benchmarks} \\ \hline
		vs.             & cores	& params   & factor \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/worstSudoku.csv}{}{\vs & \nCores & \params & \factor \\}
	\end{tabular}
	\endgroup
    \caption{Sudoku}\label{table1}
\end{subtable}
\caption{Worst Benchmark results}
\end{table}

>>>>

\begin{table}[]
\centering
\label{worstResults}
\captionsetup[subtable]{justification=centering}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{l R{0.7cm} R{1.3cm} R{1.3cm}}
		% \multicolumn{3}{c}{worst Sudoku Benchmarks} \\ \hline
		vs.             & cores & factor \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/worstSudoku-1000.csv}{}{\vs & \nCores & \factor \\}
	\end{tabular}
	\endgroup
    \caption{\sudokutest \\ 1000}\label{sudokuWorst-1000}
\end{subtable}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{l R{0.7cm} R{1.3cm} R{1.3cm}}
		% \multicolumn{3}{c}{worst Sudoku Benchmarks} \\ \hline
		vs.             & cores & factor \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/worstSudoku-16000.csv}{}{\vs & \nCores & \factor \\}
	\end{tabular}
	\endgroup
    \caption{\sudokutest \\ 16000}\label{sudokuWorst-16000}
\end{subtable}
\newline
\vspace*{1 cm}
\newline
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{l R{0.7cm} R{1.3cm} R{1.3cm}}
		% \multicolumn{3}{c}{worst Sudoku Benchmarks} \\ \hline
		vs.             & cores & factor \\ \hline
		\csvreader[head to column names]{benchmarks/sm-rm/worstRMSM-11213-32.csv}{}{\vs & \nCores & \factor \\}
	\end{tabular}
	\endgroup
    \caption{\rmtest \\ 11213 32}\label{sm-rmWorst-11213-32}
\end{subtable}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{l R{0.7cm} R{1.3cm} R{1.3cm}}
		% \multicolumn{3}{c}{worst Sudoku Benchmarks} \\ \hline
		vs.             & cores & factor \\ \hline
		\csvreader[head to column names]{benchmarks/sm-rm/worstRMSM-11213-64.csv}{}{\vs & \nCores & \factor \\}
	\end{tabular}
	\endgroup
    \caption{\rmtest \\ 11213 64}\label{sm-rmWorst-11213-64}
\end{subtable}
\newline
\vspace*{1 cm}
\newline
\begin{subtable}[t]{.32\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{l R{0.7cm} R{1.3cm} R{1.3cm}}
		% \multicolumn{3}{c}{worst Sudoku Benchmarks} \\ \hline
		vs.             & cores & factor \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-torus/worstTorus-4096.csv}{}{\vs & \nCores & \factor \\}
	\end{tabular}
	\endgroup
    \caption{\torustest (dist) 4096}\label{torusWorst-4096}
\end{subtable}
\begin{subtable}[t]{.32\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{l R{0.7cm} R{1.3cm} R{1.3cm}}
		% \multicolumn{3}{c}{worst Sudoku Benchmarks} \\ \hline
		vs.             & cores & factor \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-rm/worstRM-44497-256.csv}{}{\vs & \nCores & \factor \\}
	\end{tabular}
	\endgroup
    \caption{\rmtest \\ (dist) 44497 256}\label{dist-rmWorst-44497}
\end{subtable}
\begin{subtable}[t]{.32\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{l R{0.7cm} R{1.3cm} R{1.3cm}}
		% \multicolumn{3}{c}{worst Sudoku Benchmarks} \\ \hline
		vs.             & cores & factor \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-jacobi/worstJacobi-4253.csv}{}{\vs & \nCores & \factor \\}
	\end{tabular}
	\endgroup
    \caption{\jacobitest \\ (dist) 4253}\label{jacobiWorst-4253}
\end{subtable}
\caption{Worst Benchmark results}
\end{table}
